The design and implementation of standards-based Grid single sign-on using federated identity

### 2009-05-01 doc/sec/papers/GRID09/paper.tex
little text again

\subsection{Performance of the integration of the SAML2 SSO profile}
\label{sec:perfsaml2sso}
In our next experiment, we evaluate how does the integration of the SAML2SSO
profile affect the performance of Web Service invocation. We configure an ``echoString'' service
together with as SP (Service Provider) service, and develop a client by using
SAML2SSO related API of ARC, to invoke the ``echoString'', as well as interact with the IdP (Identity Provider).
Service and clients run on the same set of machine as Section~\ref{sec:perhedandaxis}. Meanwhile, we deploy
the Shibboleth IdP implementation on a machine equipped with 2.8GHz Intel Pentium CPU and 1GB
memory, Red Hat Enterprise Linux 5.

@@

In order to improve the performance of SAML2SSO profile, optimizing the process
between client and IdP is the correct direction, and probably one of the easiest ways is
to enhance the hardware configuration.

>>>>

\subsection{Performance of the integration of the SAML2 SSO profile}
\label{sec:perfsaml2sso}
In our next experiment, we evaluate how does the integration of the SAML2SSO
profile affect the performance of Web Service invocation. We configure an ``echoString'' service
together with as SP (Service Provider) service, and develop a client by using
SAML2SSO related API of ARC, to invoke the ``echoString'', as well as interact with the IdP (Identity Provider).
Service and clients run on the same set of machine as Section~\ref{sec:perhedandaxis}. Meanwhile, we deploy
the Shibboleth IdP implementation on a machine equipped with 2.8GHz Intel Pentium CPU and 1GB
memory, Red Hat Enterprise Linux 5. We run Shibboleth IdP (2.0.0) on Apache Tomcat(6.0.18), and
configure the JVM memory for Tomcat by setting ``CATALINA\_OPTS=-Xms16m -Xmx256m''. The Java
version is 1.6.0_07.

@@

In order to improve the performance of SAML2SSO profile, optimizing the process
between client and IdP is the correct direction. Considerting most of the performance 
characteristics for the Shibboleth IdP are determined by the Servlet Container (that is Tomcat 
in our test environment) and Java VM running it, we also increase the JVM memory for Tomcat 
by setting ``CATALINA\_OPTS=-Xms256m -Xmx1024m'', and the performance result after setting
shows little improvement.
Therefore we conclude that the easiest way is to enhance the hardware configuration.
